% !TEX encoding = UTF-8
% !TEX program = pdflatex
% !TEX spellcheck = en_GB

\documentclass[english,a4paper]{europasscv}

\ecvname{Jaime Martínez Arnau}
\ecvaddress{Málaga}
\ecvtelephone[+34 617403546]{}
\ecvemail{j.martinez.arnau@gmail.com}
%\ecvhomepage{www.myhomepage.com}
%\ecvim{AOL Messenger}{betty.smith}
%\ecvim{Google Talk}{bsmith}

\ecvdateofbirth{21 January 1975}
\ecvnationality{Spain}
%\ecvgender{Female}
%\ecvpicture[width=3.8cm]{picture.jpg}

\begin{document}
  \begin{europasscv}

  \ecvpersonalinfo

%  \ecvbigitem{Job applied for}{European project manager}

  \ecvsection{Work experience}
  
  \ecvtitle{Feb 2006 -- Present}{Software Engineer}
  \ecvitem{}{TEDIAL , Málaga, Spain}
  \ecvitem{}{I have worked seven years as a member of a development team designing and programming backend applications for \tesxtsc{Linux} servers.}
  \ecvitem{}{
  \begin{ecvitemize}
    \item Functional design, architectural design, development, testing and maintenance of a system to storage and retrieve data in/from a robotic tape library.
    \item Design and development of several tools for automating testing process of software.
    \item Maintenance and development of new features of a \tesxtsc{C\#} application.
  \end{ecvitemize}
  }
  \ecvitem{}{I work as a support engineer in a support department, having direct communication with clients. My duties involve clients system supervision, issue solving and reporting.}
  \ecvitem{}{
  \begin{ecvitemize}
    \item Analysis and development of several tools for load, transform and storage data from different kind of client repositories (\tesxtsc{XML}, \tesxtsc{Oracle database}).
    \item Analysis and development of ``ad hoc'' \tesxtsc{SQL} sentences to generate report and solve client issues.
    \item Deployment of software packages on clients production environment.
    \item Development of \tesxtsc{python} and \tesxtsc{bash} scripts to automate support tasks and problem solving.
  \end{ecvitemize}
  }

  \ecvtitle{Feb 2005 -- Feb 2006}{Developer}
  \ecvitem{}{INDRA, Málaga, Spain}
  \ecvitem{}{I have worked as a member of a development team using \textsc{Java}, \textsc{Java} Server Pages, JavaScript and \textsc{SQL} and \textsc{HTML}}
  \ecvitem{}{
  \begin{ecvitemize}
    \item Development of web application "Fidelity points Store" for a mobile phone company.
    \item Development of the corporate Intranet web portal for a mobile phone company.
    \item Deployment in the client's production environment of the developed software.
  \end{ecvitemize}
  }
%  \ecvitem{}{\ecvhighlight{Business or sector}\quad European institution}
  
  \ecvtitle{Feb 2004 -- Feb 2005}{Student intern}
  \ecvitem{}{IZAR (now Navantia), Madrid, Spain }
  \ecvitem{}{
  \begin{ecvitemize}
    \item Development of several web applications using \textsc{Java}, \textsc{Java} Server Pages, JavaScript and \textsc{SQL} and \textsc{HTML}.
    \item Design and development of a new feature for a legacy \textsc{BASIC} application.
    \item Design and development of a new input mode for a legacy \textsc{Fortran} application.
    \item Development of a Graphic User Interface using \textsc{Java} for a legacy \textsc{Fortran} application.
  \end{ecvitemize}
  }
  
  \ecvtitle{Feb 2000 -- Aug 2000}{Student intern}
  \ecvitem{}{SYSECA (subsidiary of \emph{THOMSON-CSF}), Brest, France}
  \ecvitem{}{Desing and development of a tool for the automatic code generation of web applications using \textsc{PHP}, \textsc{SQL} and \textsc{EXPRESS}.}
  
  \ecvsection{Education and training}
  
  \ecvtitlelevel{2003}{Computer engineer}{}
  \ecvitem{}{Universitat de València Estudi General, València Spain}
  \ecvitem{}{Final Year Project: ``Development of a hierarchycal communication platform \\& for the simulation of distributed virtual environments using \textsc{C++} and \textsc{CORBA}}
  
  \ecvtitle{2000}{Erasmus Programme}
  \ecvitem{}{Université de la Bretagne Occidentale, Brest France}

  
%  \pagebreak
  
  \ecvsection{Personal skills}
  \ecvmothertongue{Catalan}
  \ecvlanguageheader
  \ecvlanguage{Spanish}{Native}{Native}{Native}{Native}{Native}
  \ecvlanguage{English}{B2}{B2}{B2}{B2}{B2}
  \ecvlastlanguage{French}{B2}{B2}{B2}{B2}{B2}
  \ecvlanguagefooter
   
  \ecvblueitem{Communication skills}{
  \begin{ecvitemize}
    \item team work: I have worked in various types of teams from research and development teams to support teams.
    \item client communication: As a member of a support department I have exchanged emails and documents with clients and also assisted to call conferences using for such communications Spanish, English and Catalan.
    \item Intercultural skills: As a member of a support department I have communicated with clients from Europe, U.S.A, India, Mexico and Argentina.
  \end{ecvitemize}
  }
  
  \ecvblueitem{Organisational / managerial skills}{
  \begin{ecvitemize}
    \item I have been responsible several times with the training of the new workers arriving to  teams where I was working in.
  \end{ecvitemize}
  }
  
  \ecvblueitem{Computer skills}{
  \begin{ecvitemize}
    \item Programming Skills:  \textsc{C++}, \tesxtsc{C}, \textsc{SQL}, python, \tesxtsc{SOAP}, \textsc{HTML}, JavaScript, \textsc{Java}, \textsc{C\#}, \textsc{XML}, Bash, \tesxtsc{FUSE}, \textsc{Fortran}
    \item Repository systems: CVS, Subversion
    \item Activity tracking: JIRA
    \item Documentation: Confluence, \textsc{Wiki}, \LaTeX
  \end{ecvitemize}
  }


%  \ecvblueitem{Driving licence}{A, B}
  
  \ecvsection{Additional information}
  \ecvblueitem{Interests and Activities}{Family, Tech, Open-Source, Programming, Movies, Books.}
  
%  \ecvblueitem{Publications}{\textit{How to do Observations: Borrowing techniques from the Social Sciences to help Participants do Observations in Simulation Exercises}, Coyote EU/CoE Partnership Publication, (2002).
%}
  
  \end{europasscv}

\end{document}
